Robust Agglomeration of Labeled Neurons using 3D Skeletonization

### 2017-11-01 papers/cvpr2018/1_related_work.tex
introduction: added one sentence to explain segmentation process

Significant research in connectomics has focused on extracting information from the pixel data of the raw electron microscopy (EM) images. Building off previous work in computer vision that used normalized cuts and other graph partitioning algoirithms on images \cite{kappes2016higher,shi2000normalized,tatiraju2008image}, some of the methods apply computationally expensive graph partitioning techniques on the per-voxel images \cite{andres2012globally}. Other approaches at the per-pixel level have focused on training 2-D convolutional networks to predict membrane probabilities \cite{ciresan2012deep}. More recent work has expanded on these early networks by adding the $z$-dimension to create 3-D networks \cite{lee2015recursive}. Oftentimes these networks now predict affinities between voxels rather than membrane probabilities \cite{ronneberger2015u}. Extensive research has focused on enhancing the loss functions and optimizers for these networks \cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

@@

These neural networks produce probabilities that neighboring voxels belong to the same neuron. Many algorithms build on top of these affinities by agglomerating voxels to produce reconstructed label volumes of the EM images \cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic} (CITE NEUROPROOF, ZWATERSHED). Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation. Proofreading methods create a "human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. Flood-filling networks merge these two steps by training an end-to-end network that takes as input raw image data and produces a segmentation \cite{januszewski2016flood}. Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.

>>>>

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
Some methods apply computationally expensive graph partitioning techniques with a node per voxel~\cite{andres2012globally} following the previous work in computer vision using normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
Meanwhile, others focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}
Oftentimes these networks now produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
An extensive amount of research in computer vision, applied mathematics, and statistics evaluates the loss functions and optimizers for these networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

These above neural networks generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).

Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation. Proofreading methods create a "human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. Flood-filling networks merge these two steps by training an end-to-end network that takes as input raw image data and produces a segmentation \cite{januszewski2016flood}. Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.

@@
